### 2015-12-02 proofs/portfolio.tex
semester is almost over!
finished portfolio

@@

@@

\sum_{i = 1}^{n + 1}i^{3} &= \left(\frac{(n + 1)(n+2)}{2}\right)^{2}\\
\sum_{i = 1}^{n}i^{3} + \sum_{i = n}^{n + 1}i^{3} &= \left(\frac{(n + 1)(n+2)}{2}\right)^{2}\\
\left(\frac{n(n+1)}{2}\right)^{2} + (n + 1)^{3} &= \left(\frac{(n + 1)(n+2)}{2}\right)^{2}\ \text{By Induction Hypothesis}\\
n^{2}(n+1)^{2} + 4(n+1)^{3} &= (n+1)^{2}(n+2)^{2}\\
(n+1)^{2}(n^{2} + 4n + 4) &= (n+1)^{2}(n+2)^{2}\\
(n+2)^{2} &= (n+2)^{2}

@@

\Proof Assume that if $n$ is even, then $n^{3}$ is even.

@@

Prove that $a \equiv b(\text{mod}\ n)$ if $n|(b-a)$ is an equivalence relation on $\ZZ$.

@@

\Proof Let $n \geq 2$ and $n | (b - a)$.
Therefore $b - a  = nk,\ k\in\ZZ$.
Then $b - a \equiv 0\ mod\ n$.
It follows that $b \equiv a$, and since $mod\ n$ is an equivalence relation, $a \equiv b$ by symmetry.

@@

\Proof Assume $\sqrt{5}$ is rational.
Then $\sqrt{5} = \frac{p}{q}$ for some $p,q \in \ZZ$ with $q \neq 0$, and $p$ and $q$ have opposite parity.
It follows that $5 = \frac{p^{2}}{q^{2}}$, or $5q^{2} = p^{2}$.
If $q$ is odd, then $p$ must be even.
However, an odd number squared and multiplied by an odd number is odd, which means that $5q^{2}\in\{2k+1|k\in\ZZ\}$. 
This implies that $p^{2}$ is odd, but $p$ is even, so $p^{2}$ is even.
Therefore by contradiction, $\sqrt{5}$ must be irrational.

>>>>

\noindent\textit{\textbf{Steven Rosendahl}}\\
\textit{\textbf{Proofs Homework}}

@@

\sum_{i = 1}^{n + 1}i^{3} = \left(\frac{(n + 1)(n+2)}{2}\right)^{2}

@@

\therefore \sum_{i = 1}^{n}i^{3} + \sum_{i = n + 1}^{n + 1}i^{3} &= \left(\frac{n(n+1)}{2}\right)^{2} + (n + 1)^{3}\ \ \text{By the Induction Hypothesis}\\
&= \frac{n^{2}(n+1)^{2}}{4} + (n+1)^{3}\\
&= \frac{n^{2}(n+1)^{2}}{4} + \frac{4(n+1)^{3}}{4}\\
&= \frac{n^{2}(n+1)^{2} + 4(n+1)^{3}}{4}\\
&= \frac{(n+1)^{2}(n^{2} + 4n + 4)}{4}\\
&= \frac{(n+1)^{2}(n+2)^{2}}{2^{2}}\\
&= \left(\frac{(n+1)(n+2)}{2}\right)^{2}

@@

\Proof Assume the contrapositive: if $n$ is even, then $n^{3}$ is even.

@@

Prove that $a \equiv b(\text{mod}\ n)$ is an equivalence relation on $\ZZ$.

@@

Let $R$ be the relation $a\equiv b\ mod\ n$.\\
\textit{\textbf{Symmetric:}} Let $aRb$.
Then $a \equiv b(\text{mod}\ n)$, or $a - b = nk$ for $k\in\ZZ$.
It follows that
a &= nk + b\\
-nk &= b-a\\
nj &= b-a,\in\ZZ\\
Therefore $b \equiv a\ mod\ n$, and $R$ is symmetric.\\\\
\textit{\textbf{Reflexive:}} Let $aRa$.
Then $a \equiv a\ mod\ n$.
It follows that $n|(a-a)$, or $n|0$.
Since $n \geq 2$, $n|0$, and $R$ is reflexive.\\\\
\textit{\textbf{Transitive:}} Let $aRb$ and $bRc$.
Then $a\equiv b\ mod\ n$ and $b\equiv c\ mod\ n$.
By definition, $a-b = nk,\ k\in\ZZ$ and $b - c = nj,\ j\in\ZZ$.
Then $a-b = a-nj-c = nk$.
It follows that $a-c = nk + nj$, or $a-c = n(k + j)$.
Therefore $a\equiv b\ mod\ n$, and $R$ is transitive\\\\
Therefore $R$ is an equivalence relation.
%\Proof Let $n \geq 2$ and $n | (b - a)$.
%Therefore $b - a  = nk,\ k\in\ZZ$.
%Then $b - a \equiv 0\ mod\ n$.
%It follows that $b \equiv a$, and since $mod\ n$ is an equivalence relation, $a \equiv b$ by symmetry.

@@

\Proof Let $p$ be a prime number, and assume that $\sqrt{p}$ is rational.
Then $\sqrt{p} = \frac{n}{m}$ for $n,m \in \NN$.
It follows that $n^{2} p = m^{2}$.
We know that there are two factors of $p$, namely 1 and $p$, and that a squared number will have an even number of prime factors, since it has double the prime factors as its root.
Then $n^{2}p$ will have an odd number of prime factors, since its prime factors are the prime factors of $n^{2}$ and the number $p$.
Since $n^{2}p = m^{2}$, $m^{2}$ must also have an odd number of prime factors.
However, $m^{2}$ has an even number of prime factors.
Therefore, by contradiction, the root of a prime number is irrational.
Therefore, since 5 is prime, $\sqrt{5}$ is irrational. $\triangle$
